---
title: "Getting started"
author: "Brian Leung"
date: "2024-02-21"
categories: [news] # code # R # Python # text classification 
message: false
warning: false
---

Welcome to P-DAWG! This post introduces us to how to use Quarto (`.qmd`) to write a blog-like document that integrates `R` or `Python` code with text!

You can open a new Quarto Document (`.qmd`) in Rstudio and choose `HTML` as the format. This works just like a traditional RMarkdown file (`.rmd`).

You can copy and paste the following code to the preamble (i.e., top of the document) and fill out the details:

```         
---
title: "Give it a nice title"
author: "Your good name"
date: "today is?"
categories: [tag1, tag2, tag3...] 
message: false 
warning: false
---
```

Inside the `.qmd` document, you can type text anywhere you like. To insert a code, type "/" to select options from a drop-down menu (if you are using Visual editor mode). For example, I can insert the following `R` code chunk:

```{r}
library(tidyverse)
```

Then you can perform data analysis as usual:

```{r}
data(iris)

iris %>%
  group_by(Species) %>%
  summarize(across(where(is.numeric), mean))
```

Visualization is also easy:

```{r}
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point() +
  theme_minimal()
```

Quarto document has the advantage of being able to run `Python` code at the same time. To do that from a `RStudio` environment, you have to first install `reticulate` package in R by running `install.packages("reticulate")`

```{r}
library(reticulate)

# create a new environment 
virtualenv_create("r-reticulate")

# install SciPy
virtualenv_install("r-reticulate", "scipy")

use_virtualenv("r-reticulate")

# import SciPy (it will be automatically discovered in "r-reticulate")
scipy <- import("scipy")
```

```{python}
import scipy

```
